### 2015-05-14 corral.tex
fixes

We have implemented two different \texttt{yield} instrumentations in \whoop: \yieldcoarse and \yieldmr.
%
\yieldcoarse instruments \texttt{yield} statements in a binary fashion: if \whoop finds that a pair of entry points cannot race, then it will instrument a \texttt{yield} only after each lock and unlock statement of this pair; else if \whoop finds that a pair of entry points might race, then it will instrument context-switches after all visible operations of this pair.
%
\yieldmr performs a finer-grained instrumentation: it instruments context-switches only after each memory region that can potentially race (regardless if a pair has not been fully verified as race-free) and after each lock and unlock. In our experiments (see \S\ref{evaluation}), \yieldmr significantly outperforms \yieldcoarse.

>>>>

We have implemented two different \texttt{yield} instrumentations in \whoop: \yieldcoarse and \yieldmr.
%
The first instruments \texttt{yield} statements in a binary fashion: if \whoop proves an entry point pair as race free, then it will instrument a \texttt{yield} only after each lock and unlock statement of the pair; else if \whoop finds that a pair might race, then it will instrument a \texttt{yield} after all visible operations of the pair.
%
\yieldmr is a finer-grained instrumentation: it instruments a \texttt{yield} only after each access to a memory region that might race in the pair (regardless if the pair has not been fully proved as race-free), and after each lock and unlock. In our experiments (see \S\ref{evaluation}), \yieldmr significantly outperforms \yieldcoarse.
